 
%Summary of study. Possible ways to improve/extend analysis. Better understand ttz background? Is there anything we can say about Z, t, b, W, whatever that we can take from the study (e.g. x is difficult to detect/discriminate in such analyses due to a and b, however it can be improved by doing y). Maybe talk about what preliminary studies showed, but couldn't fully implement that idea due to whatever restriction/limitation.


The search for $tWZ$ production using 139 fb$^{-1}$ of $pp$ collision data at a centre-of-mass energy of $\sqrt{s} = 13$ TeV, recorded by the ATLAS experiment at CERN, has been presented. This thesis targeted the tetralepton final state channel. To further increase the sensitivity of $tWZ$, a combined analysis was done across the tetralepton and trilepton (studied in an independent analysis by Benjamin Warren (UCT)~\cite{ben-thesis}) channels.\\

Two SRs and Three CRs were defined. Two SRs, instead of one, were defined in order to suppress and constrain the $ZZ$ background. The definition of the $tWZ$ OF SR and the $tWZ$ SF SR take advantage of the OSSF lepton pairs which originate from the decay of a $Z$ boson, by requiring that non-$Z$ leptons in the event have the opposite and same flavours, for the $tWZ$ OF SR and $tWZ$ SF SR respectively. The resulting SRs successfully separate the $ZZ$ background, with the $tWZ$ OF SR containing around 6$\%$ of the total $ZZ$ background yield across both regions (implying that the remaining $\sim$94$\%$ is contained in the $tWZ$ SF SR). The dominant background processes, $t\bar{t}Z $ and $ZZ$ were constrained by the definition of $t\bar{t}Z$ and $ZZ$ CRs, respectively. The dominant source of fake leptons, originating from the $t\bar{t}Z$ background, was constrained by the $(tWZ)_{fake}$ CR, using the MC template method.\\

Two BDTs were implemented: an object-level BDT which aims to classify between $\ell b$ systems coming from top quarks and an event-level BDT which aims to discriminate between $tWZ$ and our major backgrounds, $t\bar{t}Z$ and $ZZ$. The output from the object-level BDT was converted to an event-level variable to be used as input to the event-level BDT. A kinematic reconstruction algorithm, 2$\nu$SM, was used to reconstruct top quarks in order to discriminate between $tWZ$ and $t\bar{t}Z$. The output from this algorithm was used as an input variable to the event-level BDT. The trained BDT was shown to discriminate well between signal and background events.\\

Using a modified ASIMOV dataset in the SRs and real data in the CRs, a blinded maximum-likelihood fit was performed across all regions in the tetralepton channel. The best-fit value of the signal strength in the tetralepton channel was,
\begin{equation}
  \mu (tWZ) =   1.91^{+0.95}_{-0.82}
\end{equation}
with an expected significance of $1.44\sigma$. The expected upper limit on the signal strength of $tWZ$ in the tetralepton channel was,

\begin{equation}
  \mu_{up}^{exp} =   1.61^{+2.35}_{-1.16}
\end{equation}

Furthermore, a blinded maximum-likelihood fit was performed across all regions across the trilepton and tetralepton channels. The best-fit value of the signal strength across both the trilepton and tetralepton channels were,

\begin{equation}
  \mu (tWZ) =   1.80^{+0.70}_{-0.65}
\end{equation}
with an expected significance of $1.61\sigma$. The expected upper limit on the signal strength of $tWZ$ across both the trilepton and tetralepton channels were,

\begin{equation}
  \mu_{up}^{exp} =   1.43^{+2.04}_{-1.03}
\end{equation}
 Although this result does not satisfy the 3$\sigma$ evidence nor the 5$\sigma$ discovery standards, this is the tightest ever constraint on the $tWZ$ process. The results in this analysis are heavily statistically limited, it is therefore expected that future analyses of this process, using larger datasets (such as that from the HL-LHC), would significantly improve the results.










